DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2019-01-27 rebuttal.tex

\begin{mdframed}[style=comment] 
We emphasize that the cost function and the SM layer is the sole difference between a neural network engineered for classification or regression.

- This should be "We emphasise that the cost function and the SM layer are the sole differences between a neural network engineered for classification or regression."
\end{mdframed}
We thank the reviewer for spotting this mistake. We have updated the manuscript.

\begin{mdframed}[style=comment] 
The goal of learning is to find the parameters $\theta$ of the neural network that minimize the risk $R(\theta) = E\left[C\left(NN_\theta(\bf{X}),\bar{\bf{Y}}\right)\right]$.

- It is the goal of training, not of learning (in common parlance anyway). Also, you should say that E[] is the expectation rather than leaving people to guess according to the next sentence.
\end{mdframed}
\todo{Assign:  @nati, @michael. \nati{@micheal, please check carefully this one, also in the text, I am not sure my notation is correct}}

According to us, the goal of training is to minimize the emprical risk, which does not contain the expectation. On the contrary, the goal of learning is to minimize the expected risk, i.e. we additionally do not want to overfit the training set. Hence we left "learning" in the text. Nevertheless, we specified the expectation operator.

@@

\begin{mdframed}[style=comment] 
The optimization is performed by computing an error gradient w.r.t. all the parameters by back-propagation and updating them with a form of stochastic gradient descent (SGD):

- This sentence is just a bit turned upside-down, it should be "The optimisation is performed by computing an error gradient w.r.t. all the parameters and updating each parameter via back propagation using a form of stochastic gradient descent (SGD):"
\end{mdframed}
\todo{Assign: @nati, @michael, \nati{again I disagree with the reviewer}}

We are not sure, we understand the reviewer. Back-propagation is a technique to compute the gradients and not to perform the update of the parameter. The latter is done with SGD. So we believe that the original formulation of our sentence is more accurate than the reviewer proposition.

@@

\begin{mdframed}[style=comment] 
As this formulation uses the standard 2D convolution, all the optimizations developed for images can be applied, what makes it computationally efficient.

- It should be "which makes it computationally efficient" instead of "what". (It's possibly "that" and not "which", but I'm never sure which ;))
\end{mdframed}
This mistake has been corrected.

\begin{mdframed}[style=comment] 
A straightforward way to impose locality in the original domain is to impose smoothness in the spectral domain, by Heisenberg’s uncertainty principle.

- What do you mean by "by Heisenberg’s uncertainty principle." That seemed to come out of nowhere. This needs explaining further.
\end{mdframed}
\todo{Assigned: @all}

\nati{The reviewer is correct. Our justification is shaddy. I am not sure how to make this clear, without writting too much. It is kind of a general consent that smoothness in one domain implies loclization in the other. The reason is that for the continuous Fourier transform, we have:
\begin{equation*}
\widehat{f(t\cdot)}(\omega)=\frac{1}{t}\hat{f}\left(\frac{\omega}{t}\right). 
\end{equation*}
Hence by concentrating $f$ in the time domain, i.e. making $t$ smaller, we also reduce the derivative of $\widehat{f(t\cdot)}$ in the spectral domain, making it smoother.
Heisenberg uncertainty principle bounds the concentration in both domains simultaneously, i.e. we have (to be checked if added to the paper)
\begin{equation*}
\text{var}({f})\text{var}({\hat{f}}) \geq \frac{1}{16 \pi^2}
\end{equation*}
Hence the theorem says that you cannot concentrate abritrarily in one domain without de-concentrating in the other.

Now the question is: how do we fix the text? Also Heisenberg does not exist in the discrete case...
}

@@

\begin{mdframed}[style=comment] 
All the above methods cannot be easily accelerated when the data lies on a part of the sphere only.

- You mention your method as part of the "above methods", but then you go on to say that using graphs does allow you to accelerate the method when data is only on part of the sphere.
\end{mdframed}
Indeed, our method can be applied only on a part or the sphere. We have corrected the text.

@@

\begin{mdframed}[style=comment] 
By interwinding graph convolutional layers and recurrent layers [65], they can for example model structured time series such as traffic on road networks [66], or recursively complete matrices for recommendation [67].

- I'm not sure what interwinding is, I guess you mean by making GC recurrent, or do you mean using GC and then RL separately? Either way there should be commas around "for example".
\end{mdframed}
\todo{Assign @michael}

\begin{mdframed}[style=comment] 
To prevent the cosmological models to be distinguished by their power spectra alone, the maps have been smoothed with a Gaussian kernel of radius 3 arcmins to remove high frequencies ($\ell$ > 1000).

- This should be "To prevent the cosmological models from being distinguished by their power spectra alone the maps have been smoothed with a Gaussian kernel of radius 3 arcmins to remove high frequencies ($\ell$ > 1000).
\end{mdframed}
We have corrected this formulation according to the reviewer suggestion.

@@

\begin{mdframed}[style=comment] 
For each class, we generate 30 simulations.

- Just mention that there are two classes again, to make it clear that "class" means "cosmology".
\end{mdframed}
\todo{Assign: @Tomek}

\begin{mdframed}[style=comment] 
That is a data augmentation scheme, as it creates more training examples than we have simulations.

- I think that you should introduce the Gaussian noise paragraph by stating that you perform data augmentation via the addition of randomly drawn Gaussian noise, rather than talking about the random noise first and then explaining that the reason is for data augmentation. ML specialists in particular will be happier with the addition of noise for DA (as will cosmologists I think).
\end{mdframed}
\todo{Assign: @all}
\nati{I think that the primary goal of adding noise is the make the problem harder, and show robust prediction, not the make the dataset larger... Hence I disagree with the reviewer. What do you think?}

The primary goal of the noise addition is the make the problem harder and show robust prediction. We use it to augment our dataset as well. Hence we believe that the correct formulation is suitable.

@@

\begin{mdframed}[style=comment] 
Probabilities are computed by the SM layer.

- As explained above, these are not probabilities, they are class predictions from the network.
\end{mdframed}
\todo{Assigned @michael}
\nati{Should we simply say "normalized network score"? I do not know...}

@@

\begin{mdframed}[style=comment] 
This standard deviation has the property to keep the energy of the signal more or less constant across layers

- Should be "of keeping" instead of "to keep". "This standard deviation has the property of keeping the energy of the signal more or less constant across layers"
\end{mdframed}
We corrected the manuscript.

\begin{mdframed}[style=comment] 
We derived this rule from the Chebyshev polynomial equations and some empirical experiments.

- This is a bit loose, can you explain further and add a citation if you didn't do the experiments yourself?
\end{mdframed}
\todo{Assign: @nati, @michael}
\nati{We would need an appendix to do that. It is the last figure of the figures notebook (expected filter). I could spend two hours and write some equation... @michael, what do you think?}

@@

\begin{mdframed}[style=comment] 
Figure 10: Random selection of 24 learned filters from the fifth spherical convolutional layer L5. Top: section. Bottom: gnomonic projection.

- There is not enough information in this caption. Can you explain that there is some obvious peak structure. I think a colourbar on the gnomonic projection would be useful too.
\end{mdframed}
\todo{Assign: @all}
\nati{The problem is that random filters are picky as well and look very similar. Should we say that? I to not think a colorbar is necessary since there is number on the top plot. Do you agree?}

We decided to not add a colorbar as scale information is already present in the top plot of the figure.

@@

\begin{mdframed}[style=comment] 
The fact that a graph representation of the disretised sphere enables an efficient convolution relaxes the iso-latitude constraint on the design of sampling schemes who aim to enable fast convolutions.

- It should be "discretised" and also "who" should be "which" (or "that", I'm not actually sure myself)
\end{mdframed}
\todo{Assign: @tomek -> \nati{I corrected it with "which". Do you agree? }}

@@

\begin{mdframed}[style=comment] 
In this case, the graph setting used through this contribution correspond to assume reflective border conditions.

- It should be "assumed". "In this case, the graph setting used through this contribution correspond to assumed reflective border conditions."
\end{mdframed}
\todo{@assign: Tomek}

\begin{mdframed}[style=comment] 
Nevertheless, dealing working with a subpart of the sphere, its border slightly affects the convolution.

- There is a superfluous word (dealing/working). I think this would read better as "Nevertheless, when working with only a part of the sphere, the border slightly affects the convolution."
\end{mdframed}
We have corrected this mistake according the reviewer suggestion.

@@

\begin{mdframed}[style=comment] 
These border effects can, however, be mitigated by padding with zeros a small area around the part of interest.

- Are they really mitigated? Surely there are still effects but you are happy with the level?
\end{mdframed}
\todo{Assign: @nati, @michael}

\begin{mdframed}[style=comment] 
Furthermore, this result is another sign that the constructed graph is able to capture the spherical structure of the HEALPix sampling.

- What does "this" refer to?
\end{mdframed}
We have clarifed the sentence as:
\begin{mdframed}[style=manuscript] 
Furthermore, the harmonics ressemblance is another sign that the constructed graph is able to capture the spherical
structure of the HEALPix sampling. 
\end{mdframed}

@@

\begin{mdframed}[style=comment] 
In a neural network setting, the fact that the graph convolution is not exactly equivariant to rotation is probably compensated by the fact that convolution kernels are learned.

- I think it might be another one of the most important points in the paper which allows you to justify why not being exact (like a spherical harmonic transform) is acceptable. If I were you I'd move this into the main body of the paper.
\end{mdframed}
\todo{Assign: @all, \nati{What do you think? I had the feeling we already have that in the main body of the paper. I cannot remember where though.}}

@@

\begin{mdframed}[style=comment] 
We then plot the result with a gnomonic projection.

- Can you add in Figure C.16 here. "We then plot the result with a gnomonic projection, as shown in Figure C.16". Also, why do you choose a gnomonic projection? In fact, with plots C.16 and C.17 I would make them a single plot (as in Figure. 10),
\end{mdframed}
We have merged the three plot a an signal figure and adapted the text reference accordingly.

@@

\begin{mdframed}[style=comment] 
We plot the section of the convoluted Kroneker.

- It should be "convolved" and probably stick with "Kroneker $\delta$". Also, why are you plotting this? What does it show? Can you go into a bit more detail?
\end{mdframed}
We build this plot in order to show the section of the filter. We believe that it might be easier to read than the gnomonic projection. We have modified the text as:
\begin{mdframed}[style=manuscript] 
For our third visualization (bottom), our goal is to plot the section of a filter. This visualization might be convenient as we theoretically have spherical filters (up to the irregularities of the sampling). The idea is to plot the section of the convolved Kroneker $\delta$.
\end{mdframed}

@@

\begin{mdframed}[style=comment] 
The error clearly converged and adding more samples will not help.

- I think this should be "converges such that" rather than "converged and". And rather than "help" I think "improve convergence further" is more descriptive.
\end{mdframed}
We changed the sentence to:
\begin{mdframed}[style=manuscript] 
The error clearly converged such that adding more samples will not improve the classifier.
\end{mdframed}

@@

\begin{mdframed}[style=comment] 
The validation error might be slightly below the training error as it is used to select hyper-parameters.

- I don't understand this statement. It could be that there is accidentally more correlation in the validation set, but I'm not sure what you mean by "it is used to select hyper-parameters" or why that would explain why there is less error in the validation set. Can you think about this further (and perhaps check for the amount of information in that data set compared to the training set)?
\end{mdframed}
\nati{
We changed the sentence as:
\begin{mdframed}[style=manuscript] 
The validation error might be slightly below the training error as the validation set is used to select hyper-parameters.
\end{mdframed}
For linear SVM, there is one hyper-parameter to tune. As we select the hyperparameter with the lowest validation error, it is possible that the validation error is lower than the training error.}

@@

- The first "is" is superfluous.
\end{mdframed}
This has been corrected.

\subsection{}

\begin{mdframed}[style=comment]

Finally, after all these little points, I just want to congratulate the authors again on a great paper. It was a pleasure reading it. I will be sure to be using this method in the near future!
\end{mdframed}
We would like to thank the reviewer again for his exceptionally detailed review. We really appreciate his effort and the time he invested in his answers. His is welcome to contact us for additional information or discussion when the publication will be over.

### 2019-01-27 scnn.tex
end of the first pass

The goal of learning is to find the parameters $\theta$ of the neural network that minimize the risk $R(\theta) = \esp \left[ C \left( NN_\theta(\X), \bar \Y \right) \right]$. In general, that expectation cannot be computed as the data distribution is unknown. We can however minimize an approximation, the empirical risk over the training set $\left\{ \left( \X_i, \bar \Y_i \right) \right\}_{i=1}^{N_{samples}}$:
\begin{equation*}
	\hat{\theta} = \argmin_\theta \sum_{i=1}^{N_{samples}} C \left(NN_\theta(\X_i), \bar \Y_i \right).
\end{equation*}
The optimization is performed by computing an error gradient w.r.t.\ all the parameters by back-propagation and updating them with a form of stochastic gradient descent (SGD):
\begin{equation*}
	\theta \leftarrow \theta - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial C \left( NN_\theta(\X_i), \bar \Y_i \right)}{\partial \theta} ,
\end{equation*}
where $\eta$ is the learning rate, and $\B$ is the set of indices in a mini-batch. Batches are used instead of single samples to gain speed by exploiting the parallelism afforded by modern computing platforms.

@@

A first approach, explored by \citep{boomsma2017spherical} for molecular modeling and \citep{su2017sphericalconv, coors2018spherenet} for omnidirectional imaging, is to use a 2D CNN on a discretization of the sphere that is a grid, such as the equirectangular projection (\figref{sphere_grids}, left panel), or a set of grids, such as the cubed-sphere defined by~\citep{ronchi1996cubed} (\figref{sphere_grids},  middle panel).
As this formulation uses the standard 2D convolution, all the optimizations developed for images can be applied, what makes it computationally efficient.
This approach is applicable to the many pixelizations that are based on a regular subdivision of a base polyhedron, such as HEALPix. Each base polyhedron then forms a grid.
Care has to be taken to handle boundary conditions: for example by padding a grid with the content of the opposite side (equirectangular) or of the neighboring grids (cubed-sphere, HEALPix). That incurs some computational losses.
For samplings that are not equal area, such as the equirectangular projection, the convolution operation should be adjusted to take the induced distortion into account \citep{su2017sphericalconv, coors2018spherenet}.

@@

All the above methods cannot be easily accelerated when the data lies on a part of the sphere only.
That is an important use case in cosmology as measurements are often partial, i.e., whole sky maps are rare.
One could still fill the unseen part of the sphere with zeros, and avoid computing empty integrals.
It is, however, not straightforward to identify empty space, and computations would still be wasted (for example on a ring that mostly contains zeros but a few measurements).
With graphs, however, computations are only performed for used pixels.
While it results in some distortions due to border effects (see \figref{border_effects} and \ref{sec:border_effects}), these can be mitigated by padding with zeros a small area around the measurements.

@@

The performance of DeepSphere is demonstrated on a discrimination problem: the classification of convergence maps into two cosmological model classes.
The experiment presented here is similar to the one by \citep{schmelze2017cosmologicalmodel}.
These maps are similar to those created with gravitational lensing techniques \citep{chang2017curvedsky}.
The two sets of maps were created using the standard cosmological model with two sets of cosmological parameters.
The classification methods were trained to predict a label from a HEALPix map.
Our Python implementation{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/DeepSphere}}} to reproduce those experiments are openly available online.
The data is available upon request from the cosmology group.\footnote{\url{http://www.cosmology.ethz.ch}}

@@

\begin{figure}[t!]
	\centering
	\includegraphics[width=\linewidth]{psd_sigma3}
	\caption{Power spectrum densities of the noiseless maps.
		To prevent the cosmological models to be distinguished by their power spectra alone, the maps have been smoothed with a Gaussian kernel of radius $3$ arcmins to remove high frequencies ($\ell>1000$).}
	\label{fig:psd_sigma3}
\end{figure}

@@

\figref{results} compares the classification accuracy of DeepSphere (FCN and CNN variants) and the two baselines across five noise levels and three sample sizes.
We indeed observe that the problem is made more difficult as the sample size decreases, and the noise increases.
As less pixels are available to make a decision about a sample, the algorithms have access to less information and make more mistakes.
As the noise increases, the useful information gets diluted in irrelevant data, i.e., the signal-to-noise ratio (SNR) diminishes.

@@

While testing the FCN and CNN variants, we made the following empirical observations.
First, training was more stable (in the sense that the loss decreased more smoothly) when using Chebyshev polynomials, as in \eqnref{graph_convolution_cheby}, rather than monomials, as in \eqnref{graph_convolution_monomial}.
Nevertheless, we could not observe a significant difference in accuracy after convergence.
Second, using $\ell_2$ regularization does not help either with performance or training of the models, mostly because the models are not over-fitting.
Third, we recommend initializing the Chebyshev coefficients with a centered Gaussian distribution with standard deviation $\sqrt{2/(F_{in} \times (K + 0.5))}$, where $K$ is the degree of the Chebyshev polynomials and $F_{in}$ the number of input channels. This standard deviation has the property to keep the energy of the signal more or less constant across layers\footnote{We derived this rule from the Chebyshev polynomial equations and some empirical experiments.}.
% Nati to Michael: The problem with the previous claim is that it depends on the non-linarity. Furthermore, does it make sense to make such a claim if we use batch norm?
Finally, we observe that scaling the Laplacian's eigenvalues between $[-a, a]$, where $0 < a \leq 1$, significantly helps in stabilizing the optimization. We use $a = 0.75$ in our experiments.

@@

The fact that a graph representation of the disretised sphere enables an efficient convolution relaxes the iso-latitude constraint on the design of sampling schemes who aim to enable fast convolutions.
In the long term, it might enable researchers to consider sampling schemes with different trade-offs, or remove the need for schemes and interpolation altogether and simply consider the positions at which measures were taken.

@@

Furthermore, this result is another sign that the constructed graph is able to capture the spherical
structure of the HEALPix sampling. In some applications, where the
exactitude of the convolution is not a requirement, such as de-noising, graph convolution could be used instead of using the spherical harmonics.
In a neural network setting, the fact that the graph convolution is not exactly equivariant to rotation is probably compensated by the fact that convolution kernels are learned.

\begin{figure}[ht!]
\centering
\includegraphics[width=\linewidth]{gaussian_filters_spectral}
\caption{Visualization of the convolution kernel $K_t(x)=e^{-\tau t x}$ in spectral domain.}
\vspace{0.3in}
\includegraphics[width=\linewidth]{gaussian_filters_gnomonic}
\caption{Visualization of the convolution kernel $K_t(x)=e^{-\tau t x}$: cross-section of the kernel through the pixels along the equator.}
\vspace{0.3in}
\includegraphics[width=\linewidth]{gaussian_filters_section}
\caption{Visualization of the convolution kernel $K_t(x)=e^{-\tau t x}$ in a gnomonic projection.}
\label{fig:gaussian_filters_visualization}
\end{figure}

In \figref{gaussian_filters_visualization}, we further leverage this example to present the three visualizations of a HEALPix graph convolution kernel.
We remember that the convolution kernel resulting from the heat diffusion is defined as $K_t(x)=e^{-\tau t x}$. For our visualization, we simply plot this function, i.e., we evaluate $K_t$
at the graph eigenvalues $\text{diag}(\bLambda)$. Note that, the lower eigenvalues $\lambda$ correspond to the lower frequencies, i.e., the spectral mode with less variation.
As a second visualization, we observe the kernel directly on the sphere. As the kernel $K_t$ is defined in the graph spectral domain, we convolve a Kroneker $\delta$  to obtain a representation on the sphere. We then plot the result with a gnomonic projection.
For our third visualization, we leverage the fact that we are working on the sphere and hence theoretically have  spherical filters (up to the irregularities of the sampling). We plot the section of the convoluted Kroneker $\delta$ .
To do so, we convolve a Kroneker $\delta$ on the nodes along the equator and use the equator for our section.
Note that, because of the small irregularities in the HEALPix sampling, the second and the third methods are subject to small variations depending on the chosen position of the Kroneker $\delta$ .

@@

One should not forget that a significant part of our analysis is done with a full sphere and that in practice we often use only part of the graph as the data may be incomplete (see \figref{example_maps}).
In this case, the graph setting used through this contribution correspond to assume reflective border conditions.
It is irrelevant when working on the complete sphere as this surface has no border. Nevertheless, dealing working with a subpart of the sphere, its border slightly affects the convolution.
As depicted in \figref{border_effects}, a filter localized near the border of a part of the sphere (via $h(\L) \b \delta_i$) no longer has an isotropic profile.
These border effects can, however, be mitigated by padding with zeros a small area around the part of interest.
Moreover, as long as the training data comes from simulations with the same applied mask, we do not expect these effects to cause problems for the analysis.

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=\linewidth]{hist_error_order2_noise1_5}
	\caption{Error w.r.t.\ the number of training samples for histogram features and the linear SVM (setting: order $o=2$, relative noise level 1.5). The error clearly converged and adding more samples will not help. The validation error might be slightly below the training error as it is used to select hyper-parameters.}
	\label{fig:hist_error_evolution}
\end{figure}

@@

The data is generated for the present analysis is based on the fast approximate N-Body simulation code \pkg{L-PICOLA} \citep{howlett2015lpicola}. For our purposes, we chose a simulation volume $V_\mathrm{sim} = (4200 \, h^{-1}\, \mathrm{Mpc})^3$, a total number of particles $N_\mathrm{part}^\mathrm{sim} = 1024^3$ placed on a mesh of size $N_\mathrm{mesh}^\mathrm{sim} = 2048^3$. The simulation was then performed 30 times with different seeds for each of the two $\Lambda$CDM cosmological models described in section \secref{data} covering a redshift range from $z = 0.1$ to $z = 0.8$. The \pkg{L-PICOLA} were performed in lightcone mode, where the simulation output is already arranged as a lightcone. Here we chose a redshift-shell thickness of $\Delta z = 0.01$.

>>>>

\nati{The goal of learning is to find the parameters $\theta$ of the neural network that minimize the risk $R(\theta) = \esp \left[ C \left( NN_\theta(\X), \bar \Y \right) \right]$, where $\esp$ is the expectation over the joint distribution $(\X, \bar \Y)$.}
In general, that expectation cannot be computed as the data distribution is unknown. We can however minimize an approximation, the empirical risk over the training set $\left\{ \left( \X_i, \bar \Y_i \right) \right\}_{i=1}^{N_{samples}}$:
\begin{equation*}
	\hat{\theta} = \argmin_\theta \sum_{i=1}^{N_{samples}} C \left(NN_\theta(\X_i), \bar \Y_i \right).
\end{equation*}
The optimization is performed by computing an error gradient w.r.t.\ all the parameters by back-propagation and updating them with a form of stochastic gradient descent (SGD):
\begin{equation*}
	\theta \leftarrow \theta - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial C \left( NN_\theta(\X_i), \bar \Y_i \right)}{\partial \theta} ,
\end{equation*}
where $\eta$ is the learning rate, and $\B$ is the set of indices in a mini-batch. Batches are used instead of single samples to gain speed by exploiting the parallelism afforded by modern computing platforms.

@@

A first approach, explored by \citep{boomsma2017spherical} for molecular modeling and \citep{su2017sphericalconv, coors2018spherenet} for omnidirectional imaging, is to use a 2D CNN on a discretization of the sphere that is a grid, such as the equirectangular projection (\figref{sphere_grids}, left panel), or a set of grids, such as the cubed-sphere defined by~\citep{ronchi1996cubed} (\figref{sphere_grids},  middle panel).
As this formulation uses the standard 2D convolution, all the optimizations developed for images can be applied, which makes it computationally efficient.
This approach is applicable to the many pixelizations that are based on a regular subdivision of a base polyhedron, such as HEALPix. Each base polyhedron then forms a grid.
Care has to be taken to handle boundary conditions: for example by padding a grid with the content of the opposite side (equirectangular) or of the neighboring grids (cubed-sphere, HEALPix). That incurs some computational losses.
For samplings that are not equal area, such as the equirectangular projection, the convolution operation should be adjusted to take the induced distortion into account \citep{su2017sphericalconv, coors2018spherenet}.

@@

\nati{All the presented methods, but our, cannot be easily accelerated when the data lies on a part of the sphere only.}
That is an important use case in cosmology as measurements are often partial, i.e., whole sky maps are rare.
One could still fill the unseen part of the sphere with zeros, and avoid computing empty integrals.
It is, however, not straightforward to identify empty space, and computations would still be wasted (for example on a ring that mostly contains zeros but a few measurements).
With graphs, however, computations are only performed for used pixels.
While it results in some distortions due to border effects (see \figref{border_effects} and \ref{sec:border_effects}), these can be mitigated by padding with zeros a small area around the measurements.

@@

The performance of DeepSphere is demonstrated on a discrimination problem: the classification of convergence maps into two cosmological model classes.
The experiment presented here is similar to the one by \citep{schmelze2017cosmologicalmodel}.
These maps are similar to those created with gravitational lensing techniques \citep{chang2017curvedsky}.
The two sets of maps were created using the standard cosmological model with two sets of cosmological parameters (see \secref{data} for details).
The classification methods were trained to predict a label from a HEALPix map.
Our Python implementation{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/DeepSphere}}} to reproduce those experiments are openly available online.
The data is available upon request from the cosmology group.\footnote{\url{http://www.cosmology.ethz.ch}}

@@

\begin{figure}[t!]
	\centering
	\includegraphics[width=\linewidth]{psd_sigma3}
	\caption{Power spectrum densities of the noiseless maps.
		To prevent the cosmological models from being distinguished by their power spectra alone, the maps have been smoothed with a Gaussian kernel of radius $3$ arcmins to remove high frequencies ($\ell>1000$).}
	\label{fig:psd_sigma3}
\end{figure}

@@

\figref{results} compares the classification accuracy of DeepSphere (FCN and CNN variants) and the two baselines across five noise levels and three sample sizes.
We indeed observe that the problem is made more difficult as the sample size decreases, and the noise increases.
As fewer pixels are available to make a decision about a sample, the algorithms have access to less information and thus cannot classify as well.
As the noise increases, the useful information gets diluted in irrelevant data, i.e., the signal-to-noise ratio (SNR) diminishes.

@@

While testing the FCN and CNN variants, we made the following empirical observations.
First, training was more stable (in the sense that the loss decreased more smoothly) when using Chebyshev polynomials, as in \eqnref{graph_convolution_cheby}, rather than monomials, as in \eqnref{graph_convolution_monomial}.
Nevertheless, we could not observe a significant difference in accuracy after convergence.
Second, using $\ell_2$ regularization does not help either with performance or training of the models, mostly because the models are not over-fitting.
Third, we recommend initializing the Chebyshev coefficients with a centered Gaussian distribution with standard deviation $\sqrt{2/(F_{in} \times (K + 0.5))}$, where $K$ is the degree of the Chebyshev polynomials and $F_{in}$ the number of input channels. This standard deviation has the property of keeping the energy of the signal more or less constant across layers\footnote{We derived this rule from the Chebyshev polynomial equations and some empirical experiments.}.
% Nati to Michael: The problem with the previous claim is that it depends on the non-linarity. Furthermore, does it make sense to make such a claim if we use batch norm?
Finally, we observe that scaling the Laplacian's eigenvalues between $[-a, a]$, where $0 < a \leq 1$, significantly helps in stabilizing the optimization. We use $a = 0.75$ in our experiments.

@@

The fact that a graph representation of the discretised sphere enables an efficient convolution relaxes the iso-latitude constraint on the design of sampling schemes which aim to enable fast convolutions.
In the long term, graphs might enable researchers to consider sampling schemes with different trade-offs, or remove the need for schemes and interpolation altogether and simply consider the positions at which measures were taken.

@@

Furthermore, the harmonics ressemblance is another sign that the constructed graph is able to capture the spherical
structure of the HEALPix sampling. In some applications, where the
exactitude of the convolution is not a requirement, such as de-noising, graph convolution could be used instead of using the spherical harmonics.
In a neural network setting, the fact that the graph convolution is not exactly equivariant to rotation is probably compensated by the fact that convolution kernels are learned.

\begin{figure}[ht!]
\centering
\includegraphics[width=\linewidth]{gaussian_filters_spectral}\\
\vspace{0.2in}
\includegraphics[width=\linewidth]{gaussian_filters_gnomonic}\\
\vspace{0.2in}
\hspace{0.3cm}\includegraphics[width=0.95\linewidth]{gaussian_filters_section}
\caption{\nati{Visualization of the convolution kernel $K_t(x)=e^{-\tau t x}$. (top) Spectral domain. (middle) Cross-section of the kernel through the pixels along the equator. (bottom) Gnomonic projection.}}
\label{fig:gaussian_filters_visualization}
\end{figure}

In \figref{gaussian_filters_visualization}, we further leverage this example to present the three visualizations of a HEALPix graph convolution kernel.
We remember that the convolution kernel resulting from the heat diffusion is defined as $K_t(x)=e^{-\tau t x}$. For our (top) visualization, we simply plot this function, i.e., we evaluate $K_t$
at the graph eigenvalues $\text{diag}(\bLambda)$. Note that, the lower eigenvalues $\lambda$ correspond to the lower frequencies, i.e., the spectral mode with less variation.
As a second visualization (middle), we observe the kernel directly on the sphere. As the kernel $K_t$ is defined in the graph spectral domain, we convolve a Kroneker $\delta$  to obtain a representation on the sphere. We then plot the result with a gnomonic projection.
\nati{For our third visualization (bottom), our goal is to plot the section of a filter. This visualization might be convenient as we theoretically have spherical filters (up to the irregularities of the sampling). The idea is to plot the section of the convolved Kroneker $\delta$.}
To do so, we convolve a Kroneker $\delta$ on the nodes along the equator and use the equator for our section.
Note that, because of the small irregularities in the HEALPix sampling, the second and the third methods are subject to small variations depending on the chosen position of the Kroneker $\delta$ .

@@

One should not forget that a significant part of our analysis is done with a full sphere and that in practice we often use only part of the graph as the data may be incomplete (see \figref{example_maps}).
In this case, the graph setting used through this contribution correspond to assume reflective border conditions.
It is irrelevant when working on the complete sphere as this surface has no border. Nevertheless, when working with a subpart of the sphere, its border slightly affects the convolution.
As depicted in \figref{border_effects}, a filter localized near the border of a part of the sphere (via $h(\L) \b \delta_i$) no longer has an isotropic profile.
These border effects can, however, be mitigated by padding with zeros a small area around the part of interest.
Moreover, as long as the training data comes from simulations with the same applied mask, we do not expect these effects to cause problems for the analysis.

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=\linewidth]{hist_error_order2_noise1_5}
	\caption{Error w.r.t.\ the number of training samples for histogram features and the linear SVM (setting: order $o=2$, relative noise level 1.5). The error clearly converged such that adding more samples will not improve the classifier. The validation error might be slightly below the training error as the validation set is used to select hyper-parameters.}
	\label{fig:hist_error_evolution}
\end{figure}

@@

The data generated for the present analysis is based on the fast approximate N-Body simulation code \pkg{L-PICOLA} \citep{howlett2015lpicola}. For our purposes, we chose a simulation volume $V_\mathrm{sim} = (4200 \, h^{-1}\, \mathrm{Mpc})^3$, a total number of particles $N_\mathrm{part}^\mathrm{sim} = 1024^3$ placed on a mesh of size $N_\mathrm{mesh}^\mathrm{sim} = 2048^3$. The simulation was then performed 30 times with different seeds for each of the two $\Lambda$CDM cosmological models described in section \secref{data} covering a redshift range from $z = 0.1$ to $z = 0.8$. The \pkg{L-PICOLA} were performed in lightcone mode, where the simulation output is already arranged as a lightcone. Here we chose a redshift-shell thickness of $\Delta z = 0.01$.
